### 2017-01-16 analysis-note-vf/Appendix.tex
some fixing

\item Exclusive $e^{4}He\gamma$ distributions
\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
The quantity &  ~~~mean & ~~~~~$\sigma$ \\
\hline
$\Delta \phi$ &  1.79405e-01 & 4.53791e-01 \\
\hline
$E_{X}$ ($e^{4}He\gamma X$) &  1.56814e-02 & 2.51492e-01 \\ 
\hline
$M^{2}_{X}$ ($e^{4}He\gamma X$) &  -2.96869e-03 & 9.10158e-03 \\ 
\hline
$pt_{X}$ ($e^{4}He\gamma X$) & 4.14664e-02 & 4.24914e-02 \\ 
\hline
$M^{2}_{X}$ ($e^{4}HeX$) &  -1.72013e-02 & 2.33988e-01 \\
\hline
 $M^{2}_{X}$ ($e\gamma X$) &  1.40066e+01 & 1.85929 \\
\hline
$\theta$ ($\gamma$,$e^{4}HeX$) &  5.08070e-01 & 4.74883e-01\\
\hline
$px_{X}$ ($e^{4}He\gamma X$) & -2.32102e-03  & 4.52945e-02\\
\hline
$py_{X}$ ($e^{4}He\gamma X$) &  -8.97351e-04 & 3.89937e-02\\ 
\hline
\end{tabular}
\caption{ The mean and sigma values of the exclusive coherent quantities drawn in figure \ref{fig:coh_exclusivty_cuts}.}
\label{Table:coh_exclusivity_cuts}
\end{center}
\end{table}

@@

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
the different bins in $x_B$ and $Q^2$. Then, the parameters of the fits were 
parametrized as a function of $x_B$ assuming that the dependence on $Q^2$ is 
negligible, figure \ref{fig:free-proton-alu}. Finally, the free proton 
asymmetries were calculated at the same measured incoherent and coherent
kinematic values.  The statistical errors on the calculated asymmetries were 
calculated using the fit errors.\\

@@

\small
\begin{landscape}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l|l|l||}
         \hline
 ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
  \hline
(1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027   &    0.1691 $\pm$ 0.0592   &  0.8042 $\pm$ 0.3248  &  0.2050 &  0.6634 &  0.1408 \\
(1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033   &    0.2081 $\pm$ 0.0738   &  0.7494 $\pm$ 0.3101  &  0.2244 &  0.6951 &  0.0543 \\ 
(2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038   &    0.2129 $\pm$ 0.0777   &  0.7268 $\pm$ 0.3206  &  0.2177 &  0.7110 &  0.0158 \\
(3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042   &    0.1765 $\pm$ 0.0676   &  0.6956 $\pm$ 0.3581  &  0.2017 &  0.6088 &  0.0868 \\
  \hline \hline  \hline                                                                                                
(1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026   &    0.1686 $\pm$ 0.0587   &  0.7045 $\pm$ 0.2913  &  0.1885 &  0.6302 &  0.0743 \\
(1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029   &    0.2122 $\pm$ 0.0740   &  0.8429 $\pm$ 0.3257  &  0.2135 &  0.8379 &  0.005  \\
(2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036   &    0.2209 $\pm$ 0.0795   &  0.6847 $\pm$ 0.2974  &  0.2170 &  0.6972 &  0.0125 \\
(2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050   &    0.1562 $\pm$ 0.0615   &  0.8457 $\pm$ 0.4661  &  0.2103 &  0.6281 &  0.2176 \\
  \hline  \hline  \hline                                                                                               
(1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027   &    0.2304 $\pm$ 0.0677   &  0.6363 $\pm$ 0.2223  &  0.2438 &  0.6013 &  0.035  \\
(2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031   &    0.2641 $\pm$ 0.0848   &  0.5700 $\pm$ 0.2177  &  0.2410 &  0.6248 &  0.0548 \\
(2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039   &    0.2200 $\pm$ 0.0791   &  0.7400 $\pm$ 0.3209  &  0.2195 &  0.7425 &  0.0025 \\
(2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054   &    0.0939 $\pm$ 0.0429   &  1.2240 $\pm$ 0.8030  &  0.1235 &  0.9311 &  0.2929 \\
  \hline  \hline  \hline                                                                                               
(1.143, 0.132, 0.096) &  0.332 $\pm$ 0.051   &    0.1821 $\pm$ 0.0528   &  1.8267 $\pm$ 0.6017  &  0.2447 &  1.3596 &  0.4671 \\
(1.423, 0.170, 0.099) &  0.353 $\pm$ 0.051   &    0.1857 $\pm$ 0.0534   &  1.9044 $\pm$ 0.6146  &  0.2518 &  1.4050 &  0.4994 \\
(1.902, 0.224, 0.107) &  0.258 $\pm$ 0.050   &    0.1835 $\pm$ 0.0524   &  1.4063 $\pm$ 0.4863  &  0.2359 &  1.0941 &  0.3122 \\
    \hline \hline  \hline                                                                                              
(1.164, 0.132, 0.095) &  0.373 $\pm$ 0.073   &    0.1819 $\pm$ 0.0529   &  2.0503 $\pm$ 0.7190  &  0.2234 &  1.6696 &  0.3807 \\
(1.439, 0.170, 0.099) &  0.267 $\pm$ 0.086   &    0.1859 $\pm$ 0.0535   &  1.4361 $\pm$ 0.6231  &  0.2432 &  1.0978 &  0.3383 \\
(1.844, 0.225, 0.107) &  0.362 $\pm$ 0.092   &    0.1830 $\pm$ 0.0522   &  1.9812 $\pm$ 0.7571  &  0.2515 &  1.4421 &  0.5391 \\
     \hline  \hline  \hline                                                                                            
(1.493, 0.177, 0.1)   &  0.326 $\pm$ 0.030   &    0.1863 $\pm$ 0.0535   &  1.7498 $\pm$ 0.5292  &  0.2453 &  1.3289 &  0.4209 \\

>>>>

\item Exclusive $e^{4}He\gamma$ distributions
\begin {table}[!h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
The quantity &  ~~~mean & ~~~~~$\sigma$ \\
\hline
$\Delta \phi$ &  1.86020e-01 & 4.64936e-01 \\
\hline
$E_{X}$ ($e^{4}He\gamma X$) &  1.48023e-02 & 2.51854e-01 \\ 
\hline
$M^{2}_{X}$ ($e^{4}He\gamma X$) &  -2.98662e-03 & 9.28645e-03 \\ 
\hline
$pt_{X}$ ($e^{4}He\gamma X$) & 4.14664e-02 & 4.24914e-02 \\ 
\hline
$M^{2}_{X}$ ($e^{4}HeX$) & -3.45128e-02 & 2.28247e-01 \\
\hline
$M^{2}_{X}$ ($e\gamma X$) & 1.39930e+01 & 1.61245 \\
\hline
$\theta$ ($\gamma$,$e^{4}HeX$) &  5.08070e-01 & 4.74883e-01\\
\hline
$px_{X}$ ($e^{4}He\gamma X$) & -2.32102e-03  & 4.52945e-02\\
\hline
$py_{X}$ ($e^{4}He\gamma X$) &  -8.97351e-04 & 3.89937e-02\\ 
\hline
\end{tabular}
\caption{ The mean and sigma values of the exclusive coherent quantities drawn in figure \ref{fig:coh_exclusivty_cuts}.}
\label{Table:coh_exclusivity_cuts}
\end{center}
\end{table}

@@

\chapter{Free proton beam-spin asymmetry interpolation} 
\label{app:free-proton-alu}
\section{Fitting the experimentally measured asymmetries} \label{fit_int} 
Following the discussion in section \ref{sec:Generalized_EMC}, comparing the 
coherent and the incoherent beam-spin asymmetries to free proton asymmetries 
reveal new information about the nuclear medium modifications. To construct 
such ratio, the published free proton asymmetries \cite{FX_BSA} have been used 
in this analysis, see figure \ref{fig:free-proton-alu}. The measured free 
proton $A_{LU}$ at $\phi = 90^{\circ}$ were fitted as a function of $-t$ for 
the different bins in $x_B$ and $Q^2$, figure \ref{fig:free-proton-alu}.  
Finally, the free proton asymmetries were calculated at the same measured 
incoherent and coherent $-t$ values from the t-dependence fit of the closest 
bin in $x_B$ and $Q^2$.  The statistical errors on the calculated asymmetries 
were calculated using the fit errors.\\

@@

\small
\begin{landscape}
\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l|l|l||}
         \hline
 ($Q^{2}$, $x_{B}$, $-t$) & EG6 $A_{LU}$ $\pm$ stat. &  Exp. fit $\pm$ stat. & Exp. $A_{LU}$ ratio   &  Model extr. & Model $A_{LU}$ ratio &  Diff. (Exp - Model)    \\
  \hline
 (1.395, 0.166, 0.407) &  0.136 $\pm$ 0.027 & 0.2061 $\pm$ 0.0092 & 0.6595 $\pm$ 0.1361 & 0.2050 & 0.6634 & -0.0039 \\
 (1.886, 0.233, 0.499) &  0.156 $\pm$ 0.033 & 0.2192 $\pm$ 0.0421 & 0.7114 $\pm$ 0.2044 & 0.2244 & 0.6951 &  0.0163 \\
 (2.338, 0.290, 0.521) &  0.154 $\pm$ 0.038 & 0.2197 $\pm$ 0.0308 & 0.7042 $\pm$ 0.2004 & 0.2177 & 0.7110 & -0.0068 \\
 (3.098, 0.379, 0.650) &  0.122 $\pm$ 0.042 & 0.2143 $\pm$ 0.0801 & 0.5727 $\pm$ 0.2907 & 0.2017 & 0.6088 & -0.0361 \\
   \hline \hline  \hline
 (1.425, 0.162, 0.397) &  0.118 $\pm$ 0.026 & 0.2124 $\pm$ 0.0091 & 0.5591 $\pm$ 0.1273 & 0.1885 & 0.6302 & -0.0711 \\
 (1.922, 0.227, 0.418) &  0.178 $\pm$ 0.029 & 0.2310 $\pm$ 0.0406 & 0.7743 $\pm$ 0.1874 & 0.2135 & 0.8379 & -0.0636 \\
 (2.354, 0.287, 0.492) &  0.151 $\pm$ 0.036 & 0.2257 $\pm$ 0.0309 & 0.6701 $\pm$ 0.1873 & 0.2170 & 0.6972 & -0.0271 \\
 (2.987, 0.390, 0.714) &  0.132 $\pm$ 0.050 & 0.1985 $\pm$ 0.0837 & 0.6654 $\pm$ 0.3802 & 0.2103 & 0.6281 &  0.0373 \\
   \hline  \hline  \hline
 (1.823, 0.213, 0.145) &  0.146 $\pm$ 0.027 & 0.2463 $\pm$ 0.0378 & 0.5950 $\pm$ 0.1447 & 0.2438 & 0.6013 & -0.0063 \\
 (2.127, 0.255, 0.282) &  0.150 $\pm$ 0.031 & 0.2259 $\pm$ 0.0182 & 0.6664 $\pm$ 0.1477 & 0.2410 & 0.6248 &  0.0416 \\
 (2.308, 0.284, 0.490) &  0.163 $\pm$ 0.039 & 0.2257 $\pm$ 0.0309 & 0.7219 $\pm$ 0.2002 & 0.2195 & 0.7425 & -0.0206 \\
 (2.406, 0.308, 1.107) &  0.115 $\pm$ 0.054 & 0.1265 $\pm$ 0.0345 & 0.9087 $\pm$ 0.4944 & 0.1235 & 0.9311 & -0.0224 \\
   \hline  \hline  \hline
 (1.143, 0.132, 0.096) &  0.282 $\pm$ 0.078 & 0.1956 $\pm$ 0.1028 & 1.4444 $\pm$ 0.8584 & 0.2447 & 1.1524 &  0.2920 \\
 (1.423, 0.170, 0.099) &  0.364 $\pm$ 0.064 & 0.1703 $\pm$ 0.0201 & 2.1366 $\pm$ 0.4529 & 0.2518 & 1.4456 &  0.6910 \\
 (1.902, 0.224, 0.107) &  0.258 $\pm$ 0.078 & 0.1814 $\pm$ 0.0822 & 1.4239 $\pm$ 0.7774 & 0.2359 & 1.0937 &  0.3302 \\
     \hline \hline  \hline
 (1.164, 0.132, 0.095) &  0.313 $\pm$ 0.069 & 0.1956 $\pm$ 0.1028 & 1.5999 $\pm$ 0.9132 & 0.2234 & 1.4011 &  0.1988 \\
 (1.439, 0.170, 0.099) &  0.237 $\pm$ 0.070 & 0.1664 $\pm$ 0.0209 & 1.4251 $\pm$ 0.4563 & 0.2432 & 0.9745 &  0.4506 \\
 (1.844, 0.225, 0.107) &  0.299 $\pm$ 0.120 & 0.1787 $\pm$ 0.0844 & 1.6736 $\pm$ 1.0599 & 0.2515 & 1.1889 &  0.4847 \\
      \hline  \hline  \hline
 (1.493, 0.177, 0.1)   &  0.331 $\pm$ 0.030 & 0.1575 $\pm$ 0.0341 & 2.1049 $\pm$ 0.4939 & 0.2453 & 1.3493 &  0.7556 \\

### 2017-01-16 analysis-note-vf/RTPC.tex
some fixing

At 6 GeV incident electron beam energy, the recoil $^{4}He$ nuclei from 
the coherent DVCS channel, have an average momentum around 200 MeV/c. CLAS 
cannot detect such low energy particles, for exemple protons are detected with 
a threshold of about 250 MeV/c, which will be even higher for helium. In order 
to detect such low-energy recoils a Radial TPC (RTPC), similar to the one used 
during the BoNuS run \cite{BONUS}, was added to CLAS. In 2009, the CLAS-EG6 
group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a 
close photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a 
schematic drawing of its internal structure. It is a 200~mm-long and 
150~mm-diameter TPC, composed of two electronically separated modules, each 
covering about 150$^{\circ}$ of the azimuthal angle. The RTPC tracks the 
charged particles through the ionization centers they leave in the gas-filled 
detection volume. Then, the ionized electrons drift under the effect of an 
electric field and are amplified by a gas electron multiplier system before to 
be detected on collection pads.

>>>>

At 6 GeV incident electron beam energy, the recoil $^{4}He$ nuclei from 
the coherent DVCS channel, have an average momentum around 200 MeV/c. CLAS 
cannot detect such low energy particles, for example protons are detected with 
a threshold of about 250 MeV/c, which will be even higher for helium. In order 
to detect such low-energy recoils a Radial TPC (RTPC), similar to the one used 
during the BoNuS run \cite{BONUS}, was added to CLAS. In 2009, the CLAS-EG6 
group \cite{proposal} has built this RTPC, figure \ref{fig:RTPC2} shows a close 
photo of the RTPC, while figure \ref{fig:RTPC_xscetion} shows a schematic 
drawing of its internal structure. It is a 200~mm-long and 150~mm-diameter TPC, 
composed of two electronically separated modules, each covering about 
150$^{\circ}$ of the azimuthal angle. The RTPC tracks the charged particles 
through the ionization centers they leave in the gas-filled detection volume.  
Then, the ionized electrons drift under the effect of an electric field and are 
amplified by a gas electron multiplier system before to be detected on 
collection pads.

### 2017-01-16 analysis-note-vf/results.tex
some fixing

Within the given uncertainties, our results show a slight dependence on 
$Q^{2}$, $x_B$, and $-t$.  More work is needed on the theoretical models to 
give predictions for $\mathcal{H}_A$.  One can see a difference between the 
precision of the extracted real and imaginary parts, indicating the fact that 
the beam-spin asymmetry is mostly sensitive to the imaginary part of the  CFF 
$\mathcal{H}_A$.

\begin{figure}[h!]
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (blue points) and 
real (red points) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of 
$Q^{2}$ (on the top right), $x_B$ (on the top left), and $t$ (on the bottom).}
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S. 
Liuti and K. Taneja \cite{simonetta_2}.} \label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_ratio.pdf}\\
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results 
   of this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
   blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown dashed 
curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}

>>>>

Within the given uncertainties, our results show a slight dependence on 
$Q^{2}$, $x_B$, and $-t$, which are in agreement with the theoretical 
calculations for $\mathcal{H}_A$.  One can see a difference between the 
precision of the extracted real and imaginary parts, indicating the fact that 
the beam-spin asymmetry is mostly sensitive to the imaginary part of the CFF 
$\mathcal{H}_A$.

\begin{figure}[h!]
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (black full squares 
in the top panel plots) and real (empty black squares in the bottom panel 
plots) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of $Q^{2}$ (on the 
left), $x_B$ (on the middle), and $t$ (on the right). The full and dashed red 
curves are calculations based on the impulse approximation from 
\cite{Vadim_priv}.  The black curves in the right plots, t-dependence plots, 
are calculations from a convolution model based on the VGG model for the 
nucleon's GPDs \cite{Guidal_priv}. The cyan curve on the top-right plot is from 
the off-shell calculations presented in section \ref{Theoretical_hypotheses} 
based on reference \cite{GonzalezHernandez:2012jv}.  }
\label{fig:HA_CFF}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_Q2_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_x_shortscenrario.pdf}\\
\includegraphics[scale=0.46]{fig_Dec2016/ALU_ratioInc_t_shortscenrario.pdf}
\caption{ The $A_{LU}$ ratio between the bound and the free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $t$ (on the bottom). The black squares are our results, the 
   green circles are the HERMES inclusive measurement \cite{HERMES_BSA} 
   results.  The blue and red curves are from an on-shell calculations from S.  
Liuti and K. Taneja \cite{simonetta_2}. The solid and dashed black curves are 
from the off-shell calculations \cite{EMC_vadim_2}.} 
\label{fig:incoh_EMC_ratio_ALU_proton}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[scale=0.9]{fig_Dec2016/Coherent_ALU_ratio.pdf}\\
\caption{The $A_{LU}$ ratio between $^4$He and free proton at 
   $\phi$~=~90$^{\circ}$, as a function of $Q^2$ (on the top), $x_B$ (on the 
   middle), and $-t$ (on the bottom). The black squares represent the results 
   of this work and the green circles are the HERMES measurements 
   \cite{HERMES_BSA}. These measurements are compared to theoretical 
   predictions from S. Liuti and K. Taneja \cite{simonetta_2}, the red and the 
   blue curves, and the model predictions from V. Guzey et al. based on the 
off-shell calculations \cite{EMC_vadim_4}, in black, purple and brown curves.}
\label{fig:coh_EMC_ratio_ALU}
\end{figure}
